---
title: "Replication"
output: html_document
---

All scripts required to reproduce the figures and tables in *Resilience for Whom? Demographic Change and the Redevelopment of the Built Environment in Puerto Rico* are contained below.

```{r echo=FALSE}
rm(list=ls())
library(knitr)
read_chunk('SCRIPTS/000-Libraries.R')
read_chunk('SCRIPTS/002-fertility_rate_projections.R') 

# Projections for all 3 scenarios
read_chunk('SCRIPTS/007-projections_20152100.R')
read_chunk('SCRIPTS/007-projections_20172100.R')
read_chunk('SCRIPTS/007-projections_20152100plus.R')

# Figures

read_chunk('SCRIPTS/figures.R')
```
# Libraries Required

```{r libraries, echo=TRUE, message = FALSE, warning = FALSE, cache=TRUE}
```

# Projecting Fertility Rates

```{r fertility, echo=TRUE, message = FALSE, warning = FALSE, cache=TRUE}

```

# Projecting PR Population 2015 - 2045 WITHOUT the Hurricane
```{r Proj2015, echo=TRUE, message = FALSE, warning = FALSE, cache=TRUE}
```

# Projecting PR Population 2017 - 2047 AFTER the Hurricane
```{r Proj2015, echo=TRUE, message = FALSE, warning = FALSE, cache=TRUE}
```

# Projecting PR Population 2015 - 2045 WITHOUT the Hurricane but with a lage increase in fertility
```{r Proj2015plus, echo=TRUE, message = FALSE, warning = FALSE, cache=TRUE}
```

# Figures

```{r Figures, echo=TRUE, message = FALSE, warning = FALSE, cache=TRUE}
```
